\documentclass{resume}

\begin{document}

\begin{Introduction}[Aaron Min Soo Kang]{1237 W Fullerton Avenue}{mkang20@depaul.edu}{669-800-9027}
\end{Introduction}

\begin{Section}[Experience]
\begin{Experience}[Software Engineer Intern]{Jun 2024 - Aug 2024}{Stryke}{LaGrange, IL} \item Resolved over 40 tickets related to software bugs, configurations, and testing. \item Implemented 3 new features for the Android application, enhancing functionality. \item Improved database query performance, reducing retrieval time from 1.5 seconds to 0.7 seconds. \item Authored the initial version of engineering documentation from scratch. 
\end{Experience}

\begin{Experience}[Software Engineer Intern]{Sep 2023 - Mar 2024}{EnCycle}{Busan, South Korea}
\item Challenged existing motion tracking software and built the only piece of software approved by the Korean Regulations Department for ballast water treatment testing system which increased accuracy of motion detection on microcontrollers by 30\%
\item Created an API facilitating communication between web applications and industrial cameras. 
\item Implemented 50+ test cases to ensure product reliability and security with the PyUnit framework.
\item Collaborated with the research team to collect and label over 1,000 images for training datasets. 
\end{Experience}

\begin{Experience}[Undergraduate Research Assistant]{Jan 2020 - Feb 2021}{Music, Imaging, Neural Dynamics (MIND) Laboratory}{Boston, Massachusetts}
\item Developed Python automation scripts to preprocess electrocardiogram (ECG) data, reducing data processing time from 2 months to 1 week. 
\item Prototyped an FDA-approved medical device that converts light frequencies into sound while working with other engineers. 
\item Administered electrocardiography experiments to 50+ participants.
\item Built a program in JavaScript that automates surveying process, which reduced experiment time by 30 minutes.
\end{Experience}
\end{Section}

\begin{Section}[Skills]
\begin{Skill}[Languages]{sql, python, go, c/c++, java}
\end{Skill}
\begin{Skill}[Frameworks/Libraries]{pandas, numpy, tensorflow, nodejs}
\end{Skill}
\end{Section}

\begin{Section}[Projects]
\begin{Experience}[Go Assembler]{June 2024}{Developer}{}
\item Built a working assembler for the Hack programming language with the Go programming language.
\item Implemented code based on system architecture and processor specifications.
\end{Experience}
\end{Section}

\begin{Section}[Education]
\begin{Education}[DePaul University, Chicago]{Expected Aug 2026}{Master's in Computer Science}
GPA: 4.0
\end{Education}
\end{Section}

\end{document}